---
title: "R Notebook"
output: html_notebook
---

```{r}
library(rpart)
```


```{r}
PrecolData <- read.csv('Cleaned_Data.csv')
```

```{r}
PrecolData
```
['SID', 'res', 'type', 'IUT', 'TransferHrs', 'hc_satv', 'hc_satm',
       'hc_satt', 'HC_SAT_New_Math', 'HC_SAT_New_EBRW', 'HC_SAT_New_Total',
       'hc_acte', 'hc_actm', 'hc_actc', 'AP_Calc_AB', 'AP_Calc_BC',
       'HS_Calc_units', 'HS_Physics_units', 'cc_hsgpa', 'cc_hsrnk', 'hs1cnty',
       'hs1state', 'First_EN_Class', 'First_EN_Term', 'First_EN_Major',
       'DegCol', 'DegMaj', 'DegTermc', 'DegGPA', 'Grad', 'GradEN', 'Last_GPA',
       'Last_Col', 'Last_Maj', 'LastTerm', 'Total_Hours', 'DropOut',
       'TookPlacement', 'Placement', 'ProbCalc', 'ProbPrecalc',
       'TransferedOutOfENGR', 'TookAP_Calc_BC', 'TookAP_Calc_AB',
       'LivesInState', 'HasLastGPA', 'HasHSGPA', 'HasHSRank', 'TookHSPhysics',
       'TookHSCalc', 'TookACT', 'TookOldSAT', 'TookNewSAT']
```{r}
set.seed(42)  # For reproducibility
train_indices <- sample(nrow(PrecolData), 0.8 * nrow(PrecolData))
train_data <- PrecolData[train_indices, ]
test_data <- PrecolData[-train_indices, ]

# Create a decision tree classifier
tree_model <- rpart(DropOut ~ . - DegMaj, data = train_data, method = "class")

# Print the decision tree
#print(tree_model)

# Make predictions on the testing data
predictions <- predict(tree_model, test_data, type = "class")

# Calculate accuracy
accuracy <- mean(predictions == test_data$DropOut)
print(paste("Accuracy:", accuracy))
```

```{r}
predictions
```

